### 2015-10-09 ThesisJo/derivations.tex
la2pdf commit - 2015:10:09	21:07:06	(Fri 9.Oct)

>>>>

\section{Mathematical Proofs}

\subsection[Proof d/dw\^{}H w\^{}HRw = 2Rw]{Proof: $\frac{\partial}{\partial\w\H} \w\H\R\w = 2\R\w$}

To prove this relation we will write the matrix operations out on index form, and 
%
\begin{align}
\w\H\R\w &= \sumb{i=1}{N}w_i^* \sumb{j=1}{N}  R_{ij} w_j \nn
&= \sumb{\substack{i=1\\i\ne k}}{N} w_i^* \sumb{j=1}{N} R_{ij} w_j + w_k^*\sumb{j=1}{N} R_{kj} w_j \nn
&= \sumb{\substack{i=1\\i\ne k}}{N} w_i^* \sumb{\substack{j=1\\j\ne k}}{N} R_{ij} w_j + w_k^*\sumb{j=1}{N} R_{kj} w_j + w_k\sumb{i=1}{N}w_i^* R_{ik} \nn
&= \sumb{\substack{i=1\\i\ne k}}{N} w_i^* \sumb{\substack{j=1\\j\ne k}}{N} R_{ij} w_j + w_k^*\sumb{j=1}{N} R_{kj} w_j + w_k^*\sumb{i=1}{N}w_i R_{ik}^* \nn
&\overset{R_{ij}=R_{ji}^*}{=} \sumb{\substack{i=1\\i\ne k}}{N} w_i^* \sumb{\substack{j=1\\j\ne k}}{N} R_{ij} w_j + 2w_k^*\sumb{i=1}{N} R_{ki} w_i
\end{align}
%
Partial differentiation with respect to $w_k^*$ then gives:
%
\begin{align}
\frac{\partial}{\partial w_k^*}\;\w\H\R\w
&= 2\sumb{i=1}{N} R_{kj} w_i
\end{align}
%
Hence, when we apply the partial differentiation as a row operation we get:
%
\begin{align}
\frac{\partial}{\partial \w^H}\;\w\H\R\w
&= \bmat{
\frac{\partial}{\partial w_1^*}\;\w\H\R\w \\
\frac{\partial}{\partial w_2^*}\;\w\H\R\w \\ \vdots \\
\frac{\partial}{\partial w_M^*}\;\w\H\R\w}
= \bmat{
2\sum_{i=1}^{N} R_{1j} w_j\\
2\sum_{i=1}^{N} R_{2j} w_j\\ \vdots \\
2\sum_{i=1}^{N} R_{Nj} w_j}
= 2\R\w
\end{align}
